---
title: "Untitled"
output: html_document
---

```{r setup}
library(tidyverse)
library(palmerpenguins)

penguins <- penguins
```


# The problem

Our summary table contains NA's, this is not what we want!

```{r}
penguins %>% 
  group_by(species) %>% 
  summarise(count = n(),
            mean_bill_length = mean(bill_length_mm))
```


# Dealing with NA's

Typically a good idea to check for NA's before any further analysis.

```{r}
penguins %>% 
```

# Example 1: Dropping NAs

One method we can use to to drop NAs completely from the data, however this may lead to other problems...

```{r}
penguins %>% 
```


# Example 2: Ignoring NA's

An alterative solution is to ignore NAs for our summary calculations

```{r}
penguins %>% 
```



# Solutions


## The problem

```{r}
penguins %>% 
  group_by(species) %>% 
  summarise(count = n(),
            mean_bill_length = mean(bill_length_mm))
```


## Dealing with NA's

Typically a good idea to check for NA's before any further analysis.

```{r}
penguins %>% 
  filter(is.na(bill_length_mm))
```

## Example 1: Dropping NAs

One method we can use to to drop NAs completely from the data, however this leads to a problem...

```{r}
penguins %>% 
  drop_na(bill_length_mm) %>% 
  group_by(species) %>% 
  summarise(count = n(),
            mean_bill_length = mean(bill_length_mm))
```


## Example 2: Ignoring NA's

An alternative solution is to ignore NAs for our summary calculations

```{r}
penguins %>% 
  group_by(species) %>% 
  summarise(count = n(),
            mean_bill_length = mean(bill_length_mm, na.rm = TRUE))
```

