---
title: "Tutorial"
output: 
  learnr::tutorial:
    theme: flatly
runtime: shiny_prerendered
---

<style type="text/css">
.ace_editor {
    font: 16px/normal 'Monaco', 'Menlo', 'Ubuntu Mono', 'Consolas', 'source-code-pro', monospace;
    direction: ltr;
    text-align: left;
}
.topicsFooter .resetButton {
    font-size: 1em;
}
</style>


```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(tidyverse)
library(palmerpenguins)
```


# The data

Our data includes details about different penguin species, including where they live and physical characteristics such as bill length, bill depth, flipper length and body mass.

```{r}
glimpse(penguins)
```

# Quick quiz

```{r quiz}
quiz(
  question("Which answer is the correct way to use `group_by()` and `summarise()`?",
    answer("group_by() + summarise()"),
    answer("summarise() %>% group_by()"),
    answer("group_by() %>% summarise()", correct = TRUE),
    answer("summarise(group_by())")
  )
)
```

# Fill in the blanks 1

Complete the code to find the **median** (`median()`) bill length for each island `island`. Your solution output should look like this:

```{r echo = FALSE, message=FALSE}
penguins %>% 
  group_by(island) %>% 
  summarise(median_bill_length = median(bill_length_mm, na.rm = TRUE))
```

```{r faded-example-1, exercise = TRUE, exercise.lines = 5}
penguins %>%  
  group_by(___) %>% 
  summarise(median_bill_length = ___(bill_length_mm, ___))
```


```{r faded-example-1-solution}
penguins %>% 
  group_by(island) %>% 
  summarise(median_bill_length = median(bill_length_mm, na.rm = TRUE))
```

If needed, you can try out your solution with the data in the chunk below:

```{r penguins-practice, exercise = TRUE, exercise.lines = 5}
penguins %>% 
```

# Fill in the blanks 2

You are interested in finding the maximum (`max()`) and minimum (`min()`) flipper length (`flipper_length_mm`) for both males and females (`sex`) on each island (`island`). Complete the code chunk below to get the following output:

```{r echo = FALSE, message=FALSE}
penguins %>% 
  group_by(island, sex) %>% 
  summarise(max_flipper_length = max(flipper_length_mm, na.rm = TRUE),
            min_flipper_length = min(flipper_length_mm, na.rm = TRUE))
```

<br>

**Hint 1:** You can group by more than one variable in the data in the following way: `data %>% group_by(group1, group2)`.

**Hint 2:** `na.rm = TRUE` can also be used in `min()` and `max()` .

<br>

```{r faded-example-2, exercise = TRUE, exercise.lines = 5}
penguins %>% 
  group_by(___, ___) %>% 
  summarise(___)
```


```{r faded-example-2-solution}
penguins %>% 
  group_by(island, sex) %>% 
  summarise(max_flipper_length = max(flipper_length_mm, na.rm = TRUE),
            min_flipper_length = min(flipper_length_mm, na.rm = TRUE))

```

If needed, you can try out your solution with the data in the chunk below:

```{r penguins-practice2, exercise = TRUE, exercise.lines = 5}
penguins %>% 

```

